\documentclass[12pt,a4paper,sans,colorlinks]{moderncv}
\moderncvcolor{blue}
\moderncvstyle{classic}

\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[english]{babel}

\usepackage{enumitem}
\newlist{cvenumerate}{enumerate}{1}
\setlist[cvenumerate]{label=[\arabic*],leftmargin=\hintscolumnwidth+\separatorcolumnwidth,labelsep=\separatorcolumnwidth}

\AtBeginDocument{\hypersetup{allcolors={color1}}}

\name{Georgi}{Shopov}
\title{Curriculum Vitae}
\address{Acad. Georgi Bonchev St., Block 2}{1113 Sofia, Bulgaria}{}
\email{gshopov@lml.bas.bg}

\begin{document}
\fancyfoot[r]{\color{color2}\pagenumberfont\strut\thepage/\pageref*{lastpage}}

\makecvtitle
\vspace*{-1cm}

\section{Research Interests}
\cvlistitem{Formal Languages and Automata Theory}
\cvlistitem{Data Structures and Algorithms}
\cvlistitem{Machine Learning}

\section{Education}
\cventry{\rlap{2020--}\hphantom{2017--2019}}{Ph.D. in Computer Science}{IICT, Bulgarian Academy of Sciences}{}{}{Thesis: \href{https://github.com/gsshopov/gsshopov.github.io/releases/download/v1.0/phd-thesis.pdf}{Finite Transducers for Representation of Language Models} \newline Supervisor: Prof. D.Sc. Stoyan Mihov}
\cventry{2017--2019}{M.Sc. in Computational Linguistics}{FMI, Sofia University}{}{}{Thesis: \href{https://github.com/gsshopov/gsshopov.github.io/releases/download/v1.0/msc-thesis.pdf}{Construction of Character-Level \(f\)-Transducers for Representation of Language Models} \newline Supervisor: Prof. D.Sc. Stoyan Mihov}
\cventry{2012--2017}{B.Sc. in Computer Science}{FMI, Sofia University}{}{}{}

\section{Professional Experience}
\cventry{2020--2025}{Assistant Professor}{IICT, Bulgarian Academy of Sciences}{}{}{}
\cventry{2018--2019}{Programmer}{IICT, Bulgarian Academy of Sciences}{}{}{}

\section{Teaching Experience}
\cventry{}{Teaching Assistant}{FMI, Sofia University}{}{}{}
\cvitem{2020--2021}{Applications of Finite Automata}
\cvitem{2017--2019}{Languages, Automata and Computability}
\cvitem{2014}{Object-Oriented Programming}
\cvitem{2013}{Introduction to Programming}

\section{Research Projects}
\cvitem{2023}{\emph{Study of a Concept for Automatic Dubbing of Documentaries}, Funded by Doli Media Studio Ltd.}
\cvitem{2023}{\emph{Consultancy for the Development of a Neural Network for Recognising Advertisements in Video Streams}, Funded by H-Tech Ltd.}
\cvitem{2021--2023}{\emph{Scientific Consultation on the Subject ``Development and Maintenance of a Platform as an Online Web-Based System for Language Resources Designed for the Use of Literary Bulgarian as the Official Language'' (BERON)}, Funded by the Ministry of Education and Science of Bulgaria}
\cvitem{2021--2022}{\emph{Development of a Bulgarian Speech Synthesiser for the Needs of People with Visual Impairments}, Funded by the Union of the Blind in Bulgaria}
\cvitem{2018--2022}{\emph{National Research Program ``Electronic Health in Bulgaria'' (NSP eHealth), Work Package 5: ``Development of a Prototype for Computer-Aided Preparation of Medical Documentation (Voice Recorder for the Bulgarian Language)''}, Funded by the Ministry of Education and Science of Bulgaria}

\section{Publications}
\begin{cvenumerate}
	\item Georgi Shopov and Stefan Gerdjikov. \newline \href{https://aclanthology.org/2024.emnlp-main.328/}{Consistent Bidirectional Language Modelling: Expressive Power and Representational Conciseness}. \newline In \emph{Proceedings of the 2024 Conference on Empirical Methods in Natural Language Processing}, 2024.
	\item Diana Geneva, Georgi Shopov and Stoyan Mihov. \newline \href{https://www.worldscientific.com/doi/10.1142/S012905412243002X}{Algorithms for Probabilistic and Stochastic Subsequential Failure Transducers}. \newline In \emph{International Journal of Foundations of Computer Science, 34}(8), 2023.
	\item Diana Geneva, Georgi Shopov, Kostadin Garov, Maria Todorova, Stefan Gerdjikov and Stoyan Mihov. \newline \href{https://www.isca-archive.org/interspeech_2023/geneva23_interspeech.html}{Accentor: An Explicit Lexical Stress Model for TTS Systems}. \newline In \emph{Proceedings of the 24th Annual Conference of the International Speech Communication Association}, 2023.
	\item Georgi Shopov, Stefan Gerdjikov and Stoyan Mihov. \newline \href{https://ieeexplore.ieee.org/document/10096566}{StreamSpeech: Low-Latency Neural Architecture for High-Quality On-Device Speech Synthesis}. \newline In \emph{Proceedings of the 2023 IEEE International Conference on Acoustics, Speech and Signal Processing}, 2023.
	\item Diana Geneva, Georgi Shopov and Stoyan Mihov. \newline \href{https://link.springer.com/chapter/10.1007/978-3-030-79121-6_11}{Algorithms for Probabilistic and Stochastic Subsequential Failure Transducers}. \newline In \emph{Proceedings of the 25th International Conference on Implementation and Application of Automata}, 2021.
	\item Diana Geneva, Georgi Shopov and Stoyan Mihov. \newline \href{https://arxiv.org/abs/2003.09364}{Composition and Weight Pushing of Monotonic Subsequential Failure Transducers Representing Probabilistic Models}. \newline In \emph{arXiv:2003.09364 [cs.FL]}, 2020.
	\item Diana Geneva, Georgi Shopov and Stoyan Mihov. \newline \href{https://link.springer.com/chapter/10.1007/978-3-030-31372-2_16}{Building an ASR Corpus Based on Bulgarian Parliament Speeches}. \newline In \emph{Proceedings of the 7th International Conference on Statistical Language and Speech Processing}, 2019.
	\item Diana Geneva and Georgi Shopov. \newline \href{https://aclanthology.org/R19-2007}{Towards Accurate Text Verbalization for ASR Based on Audio Alignment}. \newline In \emph{Proceedings of the 6th Student Research Workshop Associated with the 12th International Conference on Recent Advances in Natural Language Processing}, 2019.
\end{cvenumerate}

\end{document}